### 2024-07-25 paper.tex
about no progress on finding slodowy slices
find slodowy slices

>>>>

\subsection{Finding the previous Slodowy slices}
First we find \(\ker \ad_f\).
We have \((fX)_{ij} = i (n - i) A_{i + 1,j}\), and \((Xf)_{ij} = (j - 1) (n - (j - 1)) A_{i, j - 1}\).
So, for all \(i, j \in \{1, ..., n\}\), we have 
\[i(n - i)A_{i + 1,j} = (j - 1)(n - (j - 1))A_{1, j - 1}.\]
Taking \(j = 1\), we find that \(A_{i,1} = 0\) for \(i \geq 2\).
Then, taking \(j > 1\), we find that for \(i, j \in \{1, ..., n - 1\}\),
\[A_{i + 1, j + 1} = \frac{(j - 1)(n - (j - 1))}{i(n - i)} A_{ij}.\]
So, \(\ker\ad_f\) is the set of matrices which are upper triangular and satisfy the above condition.
\par To find the Slodowy slice associated to the previous \(\spl_2\)-triple \((E, H, F)\), we just need to find \(\ker\ad_F\).
We have 
\[[F, X] = \begin{pmatrix}
    0 & 0 \\
    f X_{21} & fX_{22}
\end{pmatrix} - \begin{pmatrix}
    0 & X_{12} f\\
    0 & X_{22} f
\end{pmatrix}.\]
Thus, \(X_{21}\) must be all zeroes except for the first row, and \(X_{12}\) must be all zeroes except for the last column, and \(X_{22} \in \ker\ad_f\).
This describes \(\ker\ad_F\).
